# (PART\*) Introduction to `ggplot2` {-}

# Preparing for the workshop

All workshop materials are found at [github.com/QCBSRworkshops/workshop03](https://github.com/QCBSRworkshops/workshop03). This includes an [R script](https://qcbsrworkshops.github.io/workshop03/book-en/workshop03-script-en.R) which contains all code chunks shown in this book.

You should also make sure you have downloaded, installed, and loaded these packages:

-    [gridExtra](http://cran.r-project.org/web/packages/gridExtra/index.html)
-    [ggplot2](http://cran.r-project.org/web/packages/ggplot2/index.html)
-    [ggsignif](http://cran.r-project.org/web/packages/ggsignif/index.html)
-    [ggdendro](http://cran.r-project.org/web/packages/ggdendro/index.html)
-    [maps](http://cran.r-project.org/web/packages/maps/index.html)
-    [mapproj](http://cran.r-project.org/web/packages/mapproj/index.html)
-    [RColorBrewer](http://cran.r-project.org/web/packages/RColorBrewer/index.html)
-    [reshape2](http://cran.r-project.org/web/packages/reshape2/index.html)
-    [GGally](http://cran.r-project.org/web/packages/GGally/index.html)
-    [patchwork](http://cran.r-project.org/web/packages/patchwork/index.html)
-    [plotly](http://cran.r-project.org/web/packages/plotly/index.html)
-    [palmerpenguins](http://cran.r-project.org/web/packages/palmerpenguins/index.html)

To install them from CRAN, run:

```{r install_pkgs, message=FALSE, warning=FALSE, include=FALSE, results=0, purl = FALSE, eval = FALSE}
# set CRAN mirror
options(repos = list(CRAN="http://cran.rstudio.com/"))

# Standard procedure to check and install packages and their dependencies, if needed.

list.of.packages <- c('gridExtra', 'ggplot2', 'ggsignif','ggdendro', 'maps', 'mapproj', 'RColorBrewer', 'reshape2', 'GGally', 'patchwork','plotly', 'palmerpenguins')

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

if(length(new.packages) > 0) {
  install.packages(new.packages, dependencies = TRUE) 
  print(paste0("The following package was installed:", new.packages)) 
} else if(length(new.packages) == 0) {
    print("All packages were already installed previously")
}

# load all packages
invisible(lapply(list.of.packages, library, character.only = TRUE))
```


```{r, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, results = 'hide'}
# Install the required packages
install.packages("gridExtra")
install.packages("ggplot2")
install.packages("ggsignif")
install.packages("ggdendro")
install.packages("maps")
install.packages("mapproj")
install.packages("RColorBrewer")
install.packages("reshape2")
install.packages("GGally")
install.packages("patchwork")
#install.packages("plotly")
install.packages("palmerpenguins")
```

To load these packages, run:

```{r, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE}
# Load the required packages
library(gridExtra)
library(ggplot2)
library(ggsignif)
library(ggdendro)
library(maps)
library(mapproj)
library(RColorBrewer)
library(reshape2)
library(GGally)
library(patchwork)
#library(plotly)
library(palmerpenguins)
```

# Learning objectives

In this workshop, we will:

**1.** Learn the basics of data visualization using R.

**2.** Learn how to find packages and resources to meet your needs.

**3.** Inspire creativity in science!

**4.** Develop an understanding of design for effective visual communication.


## Workshop outline

Today we will walk you through the basics of `ggplot2` so that you have the necessary tools to explore its use for your own projects. We will be covering the following topics:

**1.** Visualization in science

**2.** `ggplot2` mechanics: the basics

**3 ** Aesthetic mapping

**4.** Fine-tuning

**5.** Saving your plots

**6.** Conclusion

